Pixel paper structure

1. Introduction

Motivation in general terms: detector decay
Specific application: Detectors for QC in 3D printing 
Relevance of this work also for other applications: astronomy, medical imaging,...

Focus of this paper: malfunctioning pixels

Questions (from an applied perspective):
- Where do bad (malfunctioning) pixels occur? Are some areas of the detector more likely to have damage?
- Are there patterns? Is a bad pixels more or less likely to occur near another bad pixel?
- Are there different types of bad pixels such as dead, noisy, dim, not etc? How can this be classified into states?
- What are typical transitions between states? (From regular to one of the malperforming states? the other direction? from one malperforming to another?)
- What are potential causes triggering the transitions? 
- How can we detect what caused transitions?

2. Tech background & data 

Detector and X-ray technology
Details on data collections: 
- pilot data: bad pixel maps, mean and SD files)
  Perkin Elmer definitions of underperforming pixels and discussion
- experimental data: protocol for white image test data, usage data

3. Initial analysis of pilot data

Notation as lattice
Dead pixel map based analysis as point patterns
Emerging spatial patterns
Spatial distribution of means and SDs
Fluctutations within rows/columns

4. Exploratory analysis of experimental data

Means: overall and spatial distribution
SDs: overall and spatial distribution
Subpanels
Refined definition of states in the experimental data

5. Temporal analysis

Transition frequencies/probabilities
Evolution of different types of malfunctioning pixels separately
Usage data analysis
Intermediate discussion

6. Spatial analysis

Spatial statistics 101 (point patterns, F-, G-, K-functions etc)
Parametric model basics
Parametric model to adjust for spatial inhomogeneity
CSR testing using K-functions etc
Patterns: singletons, pairs, clusters, lines, bright lines etc
Above 
- for all malfunctioning pixels and 
- for subsets (dead, hot, dim etc)
Modeling: e.g. Neyman-Scott type, Matern, Thomas... models
Intermediate discussion

7. Spatio-temporal
...

8. Discussion

9. References

Spatial statistics
Technology
Other papers on dead pixels

